\package{}: an \R{} package for implemetation of the ITHIM model

### 2016-09-13 manuscript/manuscript.tex
Updates to manuscript

ITHIM is a mathematical model that integrates data on travel patterns,
physical activity, fine particulate matter, GHG emissions, and disease
and injuries. Based on population and travel scenarios. The model has
been used to calculate the health impacts of walking and bicycling
short distances usually traveled by car or driving low-emission
automobiles \cite{woodcock2013}.

The model uses comparative risk assessment through which it formulates
a change in the disease burden, resulting from the shift in the
exposure distribution from a baseline scenario to an alternative
scenario.

@@

\begin{itemize}
\item NHTS data
\item GBD data
\item ITHIM model parameters
\end{itemize}

\end{methods}

\section{Regional Example}

@@

\begin{figure}[t]
    \centerline{\includegraphics[width=0.4\textwidth]{./figures/hhsmap}}\centerline{\includegraphics[width=0.4\textwidth]{./figures/ITHIMObjs-2}}
    \caption{Change in total national DALYs for each regional transportation
estimates.
}\label{dalyFigure}
\end{figure}

\section*{Acknowledgment}

@@

%\bibliographystyle{natbib}
%\bibliographystyle{bmc_article}
\bibliographystyle{mypapers}
\bibliography{ITHIM}
\end{document}

>>>>

ITHIM is a mathematical model that integrates data on travel patterns,
physical activity, fine particulate matter, GHG emissions, and disease
and injuries. Based on population and travel scenarios. The model has
been used to calculate the health impacts of walking and bicycling
short distances usually traveled by car or driving low-emission
automobiles \cite{woodcock2013,maizlish2013}.

@@

The ITHIM model uses comparative risk assessment through which it
formulates a change in the disease burden, resulting from the shift in
the exposure distribution from a baseline scenario to an alternative
scenario.

\subsection{Data Sources}

\subsection{U.S. Metro-Regional Analysis}

@@

\begin{figure}[t]
    \centerline{\includegraphics[width=0.4\textwidth]{./figures/hhsmap}}\centerline{\includegraphics[width=0.4\textwidth]{./figures/ITHIMObjs-2}}
    \caption{Change in total national DALYs for each regional transportation
estimates.
}\label{dalyFigure}
\end{figure}
\end{methods}
\section*{Acknowledgment}

@@

%\bibliographystyle{natbib}
\bibliographystyle{bmc_article}
%\bibliographystyle{mypapers}
\bibliography{ITHIM}
\end{document}
